\documentclass[../main.tex]{subfiles}

\begin{document}

\section{Introduction}\label{sec:introduction}

This report provides an overview of the PlaceAdvisor web application, including the design of the system, software architecture, and the project's development process.

PlaceAdvisor is a platform designed to help users discover points of interest in various cities and locations. After obtaining all the relevant information about a point of interest (address, map, historical background, and more), users can also view reviews from other users and, if desired, contribute their own reviews.

The report is structured as follows:

1. \hyperref[sec:userrequirements]{\textbf{User Requirements}}: This section outlines the requirements gathered from users and stakeholders to develop the PlaceAdvisor application.

2. \hyperref[sec:userstories]{\textbf{User Stories}}: Here, you will find detailed user stories and mock-up that illustrate the expected user interactions and functionalities of the application.

3. \hyperref[sec:functionpoints]{\textbf{Function Points}}: This section provides an explanation of how function points were calculated to estimate the software size.

4. \hyperref[sec:rest]{\textbf{Rest Interface}}: Here we have the RESTful interface developed to provide access to the application's functionalities.

5. \hyperref[sec:systemarchitecture]{\textbf{System Architecture}}: Here we will provide an overview of the architecture of PlaceAdvisor, including the microservices, data storage, and external service integrations.

\end{document}
