\documentclass[../main.tex]{subfiles}

\begin{document}
\section{User Requirements}\label{sec:userrequirements}

\subsection{Introduction}
In this section, we will introduce the user requirements, that is the needs, expectations, and preferences of the people who will use a system (users). They are essential for designing and developing a system that meets the goals and solves the problems of the users. Let's start.

\subsection{User Authentication and Registration}
\textbf{Users should be able to authenticate using their Facebook account.}\\
PlaceAdvisor acknowledges the significance of user convenience and the importance of utilizing established, secure identity providers. By allowing users to authenticate using their Facebook accounts, we ensure a seamless and secure login experience, eliminating the need to create a new set of credentials for our platform.

\subsection{Integration with Google Photos}
\textbf{OAuth flow for read-only access.}\\
Users can access their Google Photos in a read-only mode, enabling them to seamlessly integrate their personal media collections into their PlaceAdvisor experience. This integration simplifies the process of sharing images and memories of their visits to points of interest.

\subsection{User Profiles}
\textbf{User's activity, basic info, and submitted feedback/reviews.}\\
User profiles serve as a central hub for personalization and user engagement. In this context, PlaceAdvisor collects basic user information and showcases their activity, highlighting their interactions with points of interest. Users also have the ability to submit feedback and reviews, fostering a sense of community and engagement.

\subsection{Points of Interest Discovery}
\textbf{Easy search by city, category, and radius.}\\
The core feature of PlaceAdvisor, point of interest discovery, is designed to be intuitive and efficient. Users can seamlessly search for points of interest by specifying key criteria such as city, category, and radius, ensuring that they can narrow down their choices to match their preferences effortlessly.\\
\textbf{Results displayed in a user-friendly list with detailed options.}\\
The search results are presented in a user-friendly list format, providing users with an overview of the available options. In addition, detailed information is readily accessible, ensuring that users can make informed decisions about their chosen points of interest.

\subsection{Detailed Place Information}
\textbf{Dedicated page with images, Wikipedia description, address, and weather.}
For each point of interest, PlaceAdvisor offers a dedicated page filled with a wealth of information. This includes vivid images, Wikipedia descriptions, precise addresses, and real-time weather data. This rich, detailed content empowers users with comprehensive insights into their selected destinations.\\
\textbf{Allows user-generated reviews with text and optional photos.}\\
The interactive aspect of PlaceAdvisor is enhanced through user-generated reviews. Users can share their experiences and insights, providing invaluable information to the community. The ability to include optional photos adds depth and authenticity to their contributions.

\subsection{Chat with Support}
\textbf{Users should be able to initiate a chat with support in real-time.}\\
In acknowledging the importance of immediate assistance, PlaceAdvisor offers real-time chat support. This feature ensures that users can reach out for help or information whenever they require it.\\
\textbf{Users should receive timely responses from customer support.}\\
Timeliness is paramount in customer support. PlaceAdvisor's commitment to user satisfaction is exemplified by our dedication to providing quick and effective responses from our support team.

\subsection{User Feedback Feature}
\textbf{Convenient form for insights and suggestions.}\\
To foster an open and responsive relationship with our users, PlaceAdvisor offers a user feedback feature. This convenient form allows users to share their insights, suggestions, and concerns, helping us to continuously enhance our platform.\\
\textbf{Users should be able to track submission status on personal info page.}\\
Users' engagement doesn't end with feedback submission. PlaceAdvisor enables users to monitor the status of their submissions directly from their personal information page, promoting transparency and accountability.

\subsection{Kibana and Elasticsearch Dashboard}

\textbf{Users should have access to a Kibana and Elasticsearch-based dashboard.}\\
PlaceAdvisor is dedicated to providing users with insights into their own interactions and preferences. The Kibana and Elasticsearch-based dashboard is designed to offer a powerful tool for users to gain deeper understanding, make data-driven decisions, and tailor their experiences on the platform.\\


In the following sections of this report, we will delve deeper into the product backlog, where these user requirements are translated into actionable user stories, and discuss the roadmap for the development of PlaceAdvisor. Additionally, we will conclude with a demonstration of the core features to illustrate how the user requirements manifest in the live application.



\end{document}